ISYE 6501

### 2022-09-07 hw2/submission.Rmd
Final changes pushed

**We repeat the above 4 steps for different k values, to find the best model(or choice of k)**

@@

df_copy$split = "train"
df_copy$split[70 < df_copy2$split_i] = "valid"
df_copy$split[85 < df_copy2$split_i] = "test"

summary_df = aggregate(df_copy,list(df_copy$split), 
          FUN = function(x) c(mean = mean(x), proportion = length(x)/nrow(df_copy)))
print.data.frame(summary_df)
```

@@

We have also kept standard deviation, such that we will be able to infer the variance of accuracy across cross folds. This is helpful because the maximum CV accuracy for different values across k varies in a very close interval (around 87.5 %) -\> see graph below

@@

Here we see that for k = 47, we get maximum average CV accuracy of 87.74%.

However, as noted above the nuance to note here is that, for k \> 30, accuracy mostly oscillates at almost the same range with delta of 0.5. But since the standard deviation of max accuracy among cross folds is 2.45 itself, this choice of k becomes a little tricky. In other words, any k value above 30 seems appropriate, as the performance separation between the models is minimal

@@

@@

```{r}
k_optimal = acc_df2[which.max(acc_df$mean_cv_accuracy),1]
acc_optimal_k = train_valid_func(df_train = df_copy, df_test = df_test, k_choice = k_optimal)
print (paste("With optimal k value, Accuracy on test =",acc_optimal_k))
```

@@

### Find optimal k using training on train and validation

#### Run the train valid func function for variety of k values

@@

However one might also argue that the optimal k values from both the approaches lie in a similar range, since any k value \>30 can be chosen from cross validation too.

>>>>

**We repeat the above 1-4 steps for different k values, to find the best model(or choice of k)**

@@

df_copy$split = "train"
df_copy$split[70 < df_copy$split_i] = "valid"
df_copy$split[85 < df_copy$split_i] = "test"

summary_df = aggregate(df_copy$R1,list(df_copy$split), 
          FUN = function(x) c(mean = mean(x), proportion = length(x)/nrow(df_copy)))
print.data.frame(summary_df)
```

@@

We have also kept standard deviation, such that we will be able to infer the variance of accuracy across cross folds. This is helpful because the maximum CV accuracy for different values across k varies in a very close interval (around 86.5 %) -\> see graph below

@@

Here we see that for k = 33, we get maximum average CV accuracy of 87.18%.

However, as noted above the nuance to note here is that, for k \> 25, accuracy mostly oscillates at almost the same range with delta of 1%. But since the standard deviation of max accuracy among cross folds is 4.47 itself, this choice of k becomes a little tricky. In other words, any k value above 25 seems appropriate, as the performance separation between the models is minimal

@@

#### Rebuild model with optimal k selected, for true test accuracy

@@

```{r}
k_optimal = acc_df[which.max(acc_df$mean_cv_accuracy),1]
acc_optimal_k = train_valid_func(df_train = df_copy, df_test = df_test, k_choice = k_optimal)
print (paste("With optimal k value, Accuracy on test =",acc_optimal_k))
```

@@

### Find optimal k using training on train and maximising accuracy on validation

#### Run the train_valid_func function for variety of k values

@@

However one might also argue that the optimal k values from both the approaches lie in a similar range, since any k value \>25 can be chosen from cross validation too.
